---
title: "National Park Service Units I have visited"
author: "Chris Hamm"
date: "`r Sys.Date()`"
output: html_document

---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

```{r prelims, echo = FALSE, message = FALSE}
library("leaflet")
library("tidyverse")
```


```{r load, echo = FALSE, message = FALSE}
visited <- read_csv("data/NP_visited.csv", col_names = TRUE, 
                    trim_ws= TRUE, 
                    col_types = list(
                      popup = col_character(), 
                      lat = col_double(), 
                      lng = col_double(), 
                      type = col_factor(levels = c("np", "nhp", "nb", "nm", "nhs", "nmp", "nmem", "nhres", "mem", "park", "nbp", "nr", "nra", "ns", "mempkwy", "nha", "nl", "nr", "pkwy", "nht", "nst", "nsr"))))
```

This map contains most of the National Park Service units that I have visited. I have omitted most of the national trails. The map is interactive. Click one the colored circles to zoom in and hover your cursor over a pin to see the name of the site. I've colored coded the sites to reflect their classification. To date, I have visited a total of `r nrow(visited)` National Park Sites.


```{r da_map, echo = FALSE, message = FALSE}
getColor <- function(visited){
  sapply(visited$type, function(type){
  if(type == "np"){
    "green"
  }else if(type == "nhs" | type == "nhp" | type == "nhres" | type == "nha" | type == "nht" | type == "nst"){
    "orange"
  }else if(type == "nbp" | type == "nb" | type == "nmp"){
      "red"
    }else if(type == "nm" | type == "mem" | type == "nmem"){
      "blue"
    }else if(type == "mempkwy" | type == "park"){
      "purple"
    }else if(type == "nra" | type == "nr" | type == "ns" | type == "nl" | type == "pkwy" | type == "nsr"){
      "purple"
    }else{
    "pink"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(visited)
)

coloring <- data.frame(type = c("National Park", "Historic", "Battlefield", "Memorial/Monument", "Recreation"), color = c("#6E8B3D", "#FF8C00", "#CD2626", "#009ACD", "#B23AEE"))

leaflet(visited) %>% 
  addTiles() %>% 
  addAwesomeMarkers(~lng, ~lat, popup = ~popup, label = ~popup, icon = icons, clusterOptions = markerClusterOptions()) %>% 
  addLegend("bottomright", colors = ~coloring$color, labels = ~coloring$type, opacity = 1, title = "Park Service unit type")
```

The `GitHub` repository, which contains the raw data and code necessary to reproduce this map, is located [here](https://github.com/butterflyology/National_Parks).

